title: "WriteUp Linear Model with prediction"
author: Ashia Graves
date: October 2024
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1 SIMS~ARM
### Scarttered Plot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```
This scatter plot indicates a positive correlation, as many of the points trend upward diagonally. The data represents the expected arm strength of the workers, suggesting that most individuals are anticipated to have arm strength ranging from 50 to 100.  

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```
The numerical results validate the positive correlation observed in the scatter plot of SIMS versus ARM. As the values increase, the correlation between the two strengthens. The data indicates a small correspondence, as the value is approaching 1.

### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation  is SIMS = 0.054563 × ARM - 4.095160.







